Model LF

### 2022-09-27 max_dp endogen stød.Rmd
commit

plot(nben_h_un_01, col= "red"); lines(nben_h_un_00, col = "blue"); 
legend("top",legend=c("Baseline", "Scenario 1"),lty=c(1,1),lwd=c(2),bty="n", col = c("blue", "red")); 
grid()

@@

@@

```{r}
plot((max_dp_01 / max_dp_00), col= "red");
legend("top", legend=c("Wage growth"),
       lty=c(1),lwd=c(2),bty="n", col = c("red"));
grid()
```

@@

```{r}
plot((pconk_ds_03 / pconk_ds_00), col= "red");
lines((yk_ds_01w / yk_ds_00), col= "blue");
lines((yk_ds_01 / yk_ds_00), col= "green");
lines((yk_ds_03 / yk_ds_00), col= "orange")
legend("top", legend=c(""),
       lty=c(1),lwd=c(2),bty="n", col = c("red"));
grid()
```

>>>>

plot(nben_h_un_03, col= "red"); lines(nben_h_un_00, col = "blue"); 
legend("top",legend=c("Baseline", "Scenario 1"),lty=c(1,1),lwd=c(2),bty="n", col = c("blue", "red")); 
grid()

@@

## Scenario 4 all shocks

```{r}
# Define add-factor list (defining shock)
constantAdjList4 <- list(

  shock_kuld_model = TIMESERIES(shock_kuld_model_shock+1 ,START=c(2006,3),  FREQ='Q'),
  shock_part_model = TIMESERIES(shock_part_model_shock+1 ,START=c(2006,3),  FREQ='Q'),
  shock_max_dp_model = TIMESERIES(shock_max_dp_model_shock+1 ,START=c(2006,3),  FREQ='Q'),
 shock_wage_ds_model = TIMESERIES(shock_wage_ds_model_shock+1 ,START=c(2006,3),  FREQ='Q')

```{r}
# Simulate the model (following shock)
Shock_4 <- SIMULATE(S_model
                    ,simType='DYNAMIC'
                    ,TSRANGE=c(2006,3,2020,1)
                    ,simConvergence=0.00001
                    ,simIterLimit=100
                    ,ConstantAdjustment=constantAdjList4
                    )
```

yk_ds_04 = Shock_4$simulation$yk_ds
emp_04 = Shock_4$simulation$emp
wage_ds_04 = Shock_4$simulation$wage_ds
ur_ds_04 = Shock_4$simulation$ur_ds
pc_ds_04 = Shock_4$simulation$pc_ds
yd_hk_ds_04 = Shock_4$simulation$yd_hk_ds
pconk_ds_04 = Shock_4$simulation$pconk_ds
komp_r_04 = Shock_4$simulation$komp_r
max_dp_04 = Shock_4$simulation$max_dp
nben_h_04 = Shock_4$simulation$nben_h
yd_hk_ds_04 = Shock_4$simulation$yd_hk_ds
ik_04 = Shock_4$simulation$ik
wage_ds_t_04 = Shock_4$simulation$wage_ds_t
nben_h_un_04 = Shock_4$simulation$nben_h_un
nl_g_04 = Shock_4$simulation$nl_g
nsben_h_04 = Shock_4$simulation$nsben_h

## Scenario 5 reg all shocks

```{r}
# Define add-factor list (defining shock)
constantAdjList5 <- list(

  shock_kuld_model = TIMESERIES(shock_kuld_model_shock+1 ,START=c(2016,1),  FREQ='Q'),
  shock_part_model = TIMESERIES(shock_part_model_shock+1 ,START=c(2016,1),  FREQ='Q'),
  shock_reg_model = TIMESERIES(shock_reg_model_shock+1 ,START=c(2016,1),  FREQ='Q'),
 shock_wage_ds_model = TIMESERIES(shock_wage_ds_model_shock+1 ,START=c(2016,1),  FREQ='Q')

```{r}
# Simulate the model (following shock)
Shock_5 <- SIMULATE(S_model
                    ,simType='DYNAMIC'
                    ,TSRANGE=c(2006,3,2020,1)
                    ,simConvergence=0.00001
                    ,simIterLimit=100
                    ,ConstantAdjustment=constantAdjList5
                    )
```

yk_ds_05 = Shock_5$simulation$yk_ds
emp_05 = Shock_5$simulation$emp
wage_ds_05 = Shock_5$simulation$wage_ds
ur_ds_05 = Shock_5$simulation$ur_ds
pc_ds_05 = Shock_5$simulation$pc_ds
yd_hk_ds_05 = Shock_5$simulation$yd_hk_ds
pconk_ds_05 = Shock_5$simulation$pconk_ds
komp_r_05 = Shock_5$simulation$komp_r
max_dp_05 = Shock_5$simulation$max_dp
nben_h_05 = Shock_5$simulation$nben_h
yd_hk_ds_05 = Shock_5$simulation$yd_hk_ds
ik_05 = Shock_5$simulation$ik
wage_ds_t_05 = Shock_5$simulation$wage_ds_t
nben_h_un_05 = Shock_5$simulation$nben_h_un
nl_g_05 = Shock_5$simulation$nl_g
nsben_h_05 = Shock_5$simulation$nsben_h

@@

```{r}
plot((max_dp_04 / max_dp_00), col= "red");
legend("top", legend=c("Wage growth"),
       lty=c(1),lwd=c(2),bty="n", col = c("red"));
grid()
```

@@

```{r}
plot((yk_ds_01b / yk_ds_00), col= "red", ylim= c(0.995,1.005));
lines((yk_ds_05 / yk_ds_00), col= "blue");
```

```{r}
plot((yk_ds_01 / yk_ds_00), col= "red", ylim= c(0.99,1.01));
lines((yk_ds_01w / yk_ds_00), col= "blue");
lines((yk_ds_02 / yk_ds_00), col= "green");
lines((yk_ds_04 / yk_ds_00), col= "orange");
legend("top", legend=c(""),
       lty=c(1),lwd=c(2),bty="n", col = c("red"));
grid()
```
